---
title: "Model Results"
format: html
execute:
  warning: false
  echo: false
  message: false
---

```{r}
#| label: setup
#| message: false
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
data <- read_csv("depression_anxiety_data.csv")
```


```{r}
#|cache: true
data_cleaned <- data |>
  mutate(depression_diagnosis = factor(depression_diagnosis, levels = c(FALSE, TRUE)),
         gender = ifelse(gender == "male", 0, 1)) |>
  drop_na(phq_score, gender, age)

d_model_new <- brm(depression_diagnosis ~ phq_score + gender + age, 
                    data = data_cleaned,
                    family = bernoulli(),
                    refresh = 0, 
                    silent = 2, 
                    seed = 9)


fixef(d_model_new)

```

### Interpretting the Results:
$$
\text{Log-Odds}(\text{Depression\ Diagnosis}) = \beta_0 + \beta_1 \times \text{PHQ\ score} + \beta_2 \times \text{gender} + \beta_3 \times \text{age}
$$

The following interpretations apply to college students aged 18 to 30, assuming all other factors are held constant:

- **Public Health Questionaire Score:**
  - **Odds Ratio**: 
    $$
    e^{\beta_1} = e^{0.13} \approx 1.14
    $$
  - **Explanation**: Each 1-point increase in the PHQ score raises the odds of a depression diagnosis by approximately 14%.

- **Gender:**
  - **Odds Ratio**: 
    $$
    e^{\beta_2} = e^{0.37} \approx 1.45
    $$
  - **Explanation**: Being female increases the odds of a depression diagnosis by about 45% compared to being male.

- **Age:**
  - **Odds Ratio**: 
    $$
    e^{\beta_3} = e^{0.15} \approx 1.16
    $$
  - **Explanation**: Each additional year of age increases the odds of a depression diagnosis by about 16%.

- **Intercept:**
  - **Odds Ratio**: 
    $$
    e^{\beta_0} = e^{-6.72} \approx 0.001
    $$
  - **Explanation**: The intercept represents the baseline odds of depression diagnosis when all predictors are zero.
 

